Optimal (Multiway) Spatial Joins

### 2024-06-07 msj.tex
yufei

\begin{proof}
    Set $h' = \bm{t}[k-2]$. By the definition of a trimmed segment, there exists a rectangle $r_{k-2} \in R_{k-2}$ covering both endpoints of $h$. Thus, the effective horizontal segment of $\bm{t}$ (defined in Section~\ref{sec:hv:type2}) --- which must be contained in $h'$ --- must also be covered by $r_{k-2}$. Hence, $\contain_{R_{k-2}}(\bm{t})$ contains $r_{k-2}$ and thus cannot be empty.
\end{proof}

@@

Next, we argue that $r_{k-2}\in \contain_{R_{k-2}}(\bm{t})$. Let $p'$ be the left endpoint of $h$. Because$h' \cap v = h \cap v = p$, the effective horizontal segment of $\bm{t}$ is the segment $p'p$. To prove $r_{k-2} \in \contain_{R_{k-2}}(\bm{t})$, we need to explain why $r_{k-2}$ covers this segment. This is true because:

>>>>

\begin{proof}
    Set $h' = \bm{t}[k-2]$. By the definition of a trimmed segment, there exists a rectangle $r_{k-2} \in R_{k-2}$ covering both endpoints of $h'$. Thus, the effective horizontal segment of $\bm{t}$ (defined in Section~\ref{sec:hv:type2}) --- which must be contained in $h'$ --- must also be covered by $r_{k-2}$. Hence, $\contain_{R_{k-2}}(\bm{t})$ contains $r_{k-2}$ and thus cannot be empty.
\end{proof}

@@

Next, we argue that $r_{k-2}\in \contain_{R_{k-2}}(\bm{t})$. Let $p'$ be the left endpoint of $h$. Because$h' \cap v = h \cap v = p$, the effective horizontal segment of $\bm{t}$ is the segment $p'p$. To prove $r_{k-2} \in \contain_{R_{k-2}}(\bm{t})$, we need to explain why $r_{k-2}$ covers segment $p'p$. This is true because:
